Some lessons after the formalization of the ctm approach to forcing \thanks{Supported by Secyt-UNC project 33620180100465CB and Conicet.}

### 2022-04-05 JSL/lessons.tex
Starting the section on forcing. Liquid Tensor Experiment refs
Trimming list of lessons

\subsection{Ask about your project}
\url{https://mathoverflow.net/q/265435/66044}

Disclaimer: It may be useless.

\subsection{Read about what is done}
\begin{enumerate}
\item Related work at that moment.
\item Precise enumeration of what \session{ZF-Constructible} had.
\end{enumerate}

@@

\subsection{Plan before formalizing}
\begin{enumerate}
\item We should had better used predicates for the forcing posets'
  order relations (the way DSL is written), and go for class forcing
  (with $\PP$ a definable subset of $M$). The latter change seems to be
  easy, but the former doesn't.

  “Sometimes it felt like sculpting on marble: The fear of having
  carved too deep and hence needing to change the whole stone!”
\end{enumerate}

\subsection{In case of doubt, formalize it}
\begin{enumerate}
\item Example: the abstract of the CLAM2021 talk.
\end{enumerate}

@@

\subsection{Beware of the “Code fever”}
\begin{enumerate}
\item “We know that doing math is fun---formalization is like DRUGS”
\item Feeling of accomplishment after seeing your writings
  validated beyond reasonable doubt.
\item One easily forgets about the “Power of the Board.”
\end{enumerate}

>>>>

\subsection{Plan before formalizing}
\begin{enumerate}
\item Ask about your project
  \url{https://mathoverflow.net/q/265435/66044}

  Disclaimer: It may be useless.
\item Antecedents: Precise enumeration of what \session{ZF-Constructible} had.

\item We should had better used predicates for the forcing posets'
  order relations (the way DSL is written), and go for class forcing
  (with $\PP$ a definable subset of $M$). The latter change seems to be
  easy, but the former doesn't.

  “Sometimes it felt like sculpting on marble: The fear of having
  carved too deep and hence needing to change the whole stone!”

  Note: This is in direct contradiction with “code fever”
  (\ref{sec:beware-code-fever} below).
\end{enumerate}

@@

@@

\subsection{Beware of the “Code fever”}\label{sec:beware-code-fever}
\begin{enumerate}
\item “We know that doing math is fun---formalization is like DRUGS”
\item Feeling of accomplishment after seeing your writings
  validated beyond reasonable doubt.
\item One easily forgets about the “Power of the Board.”
\end{enumerate}
